Tool-driven Revolutions in Archaeological Science

### 2018-09-10 analysis/paper/jcaa-paper.Rmd
typos

We have shown a bibliometric analysis that reveals substantial change in the use of the R programming languages in ecology.  We saw that ecological and evolutionary sciences have strongly embraced R in their publications. Archaeologists have more recently taken up R, but to a much lesser degree, so far, than what we see in the other fields, most commonly in more scientific aspects of archaeology. We also identified a small sub-set of archaeology papers that use R to make their work fully reproducible and could identify an advantage of citing R for researchers as it leads to being referenced more often.

There is great potential for archaeologists to make their work reproducible using R and related tools, and we think this is a much needed shift in computational archaeology - linking the digital and computational times to  older practices of sharing data and methods. We therefore presented our freely available R package, rrtools, which is designed to make it easy for researchers in archaeology and other fields to make their research reproducible. We hope this will help to realise some of the potential to make computational archaeological research more open and reproducible speed the transfer of new results and methods throughout the research community without barriers due to resource availabilty, and in this way encourage researchers to adhere to the scientific process.

>>>>

We have shown a bibliometric analysis that reveals substantial change in the use of the R programming languages in ecology. We saw that ecological and evolutionary sciences have strongly embraced R in their publications. Archaeologists have more recently taken up R, but to a much lesser degree, so far, than what we see in the other fields, and most commonly in more scientific aspects of archaeology. We also identified a small sub-set of archaeology papers that use R to make their work fully reproducible and could identify an advantage of citing R for researchers as it leads to being referenced more often.

There is great potential for archaeologists to make their work reproducible using R and related tools, and we think this is a much needed shift in computational archaeology - linking the digital and computational times to  older practices of sharing data and methods. We therefore presented our freely available R package, rrtools, which is designed to make it easy for researchers in archaeology and other fields to make their research reproducible. We hope this will help to realise some of the potential to make computational archaeological research more open and reproducible, speed the transfer of new results and methods throughout the research community without barriers due to resource availabilty, and also in this way encourage researchers to adhere to the scientific process.
